\center \fontsize{18}{20} \selectfont Revealing the Landscape of Globally Color-Dual Multi-loop Integrands

### 2023-09-28 notes/2loopNLSM.tex
looks good - my hands are off

>>>>

\subsection{Chern-Simons theory}
\label{sec:CSTheory}
The final theory that is unified by the semi-abelian Yang-Mills construction is Chern-Simons (CS) theory. As we will show below, plugging in appropriate on-shell states to the semi-YM numerators that we constructed in the text will produce precisely the kinematic numerators for CS theory. Much like SDYM and ZM theory, the CS action as a preferred integer dimension of $D=3$,
\be
S_{\text{CS}} = \int d^3 x \,\text{tr}\left[\epsilon^{\mu\nu\rho} \left(A_\mu \partial_\nu A_\rho + \frac{2}{3}A_{\mu}A_{\nu}A_{\rho}\right)\right]
\ee
where $\epsilon^{\mu\nu\rho}$ is a 3D Levi-Civita symbol. The color-dual properties of this theory was previously studied in ref.~\cite{Ben-Shahar:2021zww}, which demonstrated that color-kinematics duality is manifest off-shell. The Feynman rules for this theory can be pulled directly from the action, giving the following color-stripped three-point vertex and propagator:
\be\label{CSFrule}
\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} = \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2\varepsilon^{\rho}_3 \qquad \qquad \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
\ee
At first glance, this seems far removed from the semi-abelian Yang-Mills analogs in \cref{semiYMvert} and \cref{semiYMprop}. After all, semi-YM makes no reference to an anti-symmetric 3-tensor, and doesn't even have the mass-dimension as the CS theory vertex. However, to construct the full on-shell amplitudes of CS theory, we must plug in the Fourier transforms of the on-shell currents, $\bar{\varepsilon}(p)$, as described in ref.~\cite{Ben-Shahar:2021zww}. These are related to the polarizations, $\varepsilon_i$, of the Feynman rules above as follows:
\be
\varepsilon^{\mu}(p) = \epsilon^{\mu\nu\rho} p^\nu \bar{\varepsilon}^\rho(p)
\ee
With this definition of the on-shell states, it is clear how the Feyman rules of \cref{CSFrule} are related to those of \cref{semiYMvert} and \cref{semiYMprop} -- we must simply canonicalize the CS kinetic term by absorbing $ \epsilon^{\mu\nu\rho} k^\rho$ into the definition of the three-point vertex:
\be
 \propFrule{$A^\nu$}{$A^\mu$}{$k \rightarrow $}{nhpRed} = \frac{i}{k^2} \epsilon^{\mu\nu\rho} k^\rho
\quad \longrightarrow \quad  \propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}
\ee
This has the effect of orienting the three-point vertex of \cref{CSFrule}, by making the replacement $\varepsilon_i \rightarrow \epsilon^{\mu\nu\rho} k_i^\nu \bar{\varepsilon}^\rho_i$ on one of the legs:
\begin{align}
\cubic{hgrey0}{nhpRed}{}{nhpRed}{}{nhpRed}{} =  \epsilon^{\mu\nu\rho} \varepsilon^{\mu}_1\varepsilon^{\nu}_2 (\epsilon^{\rho \alpha \beta} k_3^\alpha \bar{\varepsilon}^\beta_3) =    (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{align}
where we have used the identity, $\epsilon^{\mu\nu\rho}\epsilon^{\rho\alpha\beta} = \eta^{\mu \alpha} \eta^{\nu \beta} -  \eta^{\mu \beta} \eta^{\nu \alpha}$. Thus as desired, the CS vertex is precisely the three-point vertex of \cref{semiYMvert}. Moreover, in this form it is also clear how to map the $D$-dimensional amplitudes of semi-YM to the 3D observables of CS theory, one simply makes the following replacement on all the external states of semi-abelian YM, 
\be
\varepsilon^\mu_i \rightarrow \epsilon^{\mu\nu\rho} k^\nu_i \bar{\varepsilon}^\rho_i \qquad\qquad  \bar{\varepsilon}_i^\mu \rightarrow \bar{\varepsilon}^\mu_i
\ee
Upon making this replacement, one can map the amplitudes of $D$-dimensional semi-YM to CS theory defined in $D=3$, $\mathcal{A}^{\text{semi-YM}}\rightarrow \mathcal{A}^{\text{CS}}$. While this may seem like a marginal gain at tree-level, by using our $D$-dimensional construction at one-loop, the manifestly color-dual integrands of \cref{SDYMnGon} can resolve regularization ambiguity of CS theory due to its explicit dependence on $D=3$. For more background on CS theory, we refer the reader to ref.~\cite{Ben-Shahar:2021zww}.
